Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Recovery, and Limits to Cosmology

### 2017-02-17 paper1.tex
a little quantification
this is an old change I'm just getting around to committing.
a couple more edits. needs more...

\section{Data and Mock Observations}\label{sec:Data}
In this section, we describe the data products and the techniques used to replicate the HETDEX survey. We use the information from a large mock galaxy catalog enhanced by the emission line properties of galaxies detected by the \textit{Sloan Digital Sky Survey} (SDSS; \citealt{Blanton2001a}) to create a realistic ``sky'' and ``observe'' it with a HETDEX-like observing strategy.

@@

Galaxy $M_r$ luminosities are added to the velocity peaks using Sub-halo Abundance Matching (ShAM) \citep{Reddick2013}, and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) assign luminosities in the other bands. A $M_r$-density-SED relation is created using a SDSS training set, and for each mock galaxy the SED of a randomly selected training set galaxy which has a similar $M_r$ and density is assigned. The assigned SED is also used to determine additional $ugiz$ magnitudes. The result is a mock catalog containing 238 million galaxies with $\sdssr < 29$ mag and $z \leq 8.7$.

@@

\subsection{Conditional {\rm[\ion{O}{II}]} Flux Probability Distribution Functions}\label{sec: oii luminosity}
We use the SDSS Data Release 12 \citep{Alam2015} catalogs to assign [\ion{O}{II}] emission line strengths to the galaxies in the Buzzard catalog. We use 503,094 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{II}] line flux of at least one. Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies, and the following SQL query selects the appropriate galaxies:
\begin{lstlisting}[language=SQL]
SELECT GAL.objid,
SELECT GAL.objid,
       GAL.u,
       GAL.err_u,
       GAL.g,
       GAl.err_g,
       GAL.r,
       GAL.err_r,
       GAL.i,
       GAl.err_i,
       GAL.z,
       GAL.err_z,
       g.oii_3726_flux,
       g.oii_3726_flux_err,
       s.z AS redshift
INTO   mydb.sdsstraining
FROM   galaxy AS GAL
       JOIN specobj AS s
         ON s.bestobjid = GAL.objid
       JOIN galspecline AS g
         ON g.specobjid = s.specobjid
WHERE  oii_3726_flux > oii_3726_flux_err
       AND oii_3726_flux_err > 0
       AND s.z BETWEEN 0.02 AND 0.2
       AND s.class = 'GALAXY'
       AND s.zwarning = 0
\end{lstlisting}

To assign an [\ion{O}{II}] luminosity to each galaxy in our catalog, we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy. We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{II}] luminosities, the right panel of Figure \ref{fig: oii sdss}. Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{II}] luminosity based on the distribution of SDSS galaxies in that bin. In very few cases (1.3\% of galaxies), the $g-r$ and $M_r$ magnitudes of the galaxies in the Buzzard catalog do not overlap with the distributions in SDSS. For these objects, we assign them zero [\ion{O}{II}] flux, but this has no impact on our analysis. For catalog galaxies with have very few ($1\leq N<10$) SDSS galaxies in their respective bin, we assign it the mean [\ion{O}{II}] flux.

@@

\subsection{Recovery of Cluster Members}
\begin{figure*}
	\includegraphics[width=0.8\textwidth]{figures/recovery.pdf}
	\caption[Recovery fractions for the Targeted and Survey observations.]{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and true cluster mass for the Targeted and Survey observing strategies. The Targeted observations include HETDEX line and continuum flux limits and have a unity fill factor. The Survey observations again include HETDEX-like flux limits but a HETDEX-like fill factor, 1/4.5. We require at least five galaxies to be detected for a cluster to be recovered. The shading indicates the mean recovery fraction for clusters within each small bin of redshift and cluster mass. We find a significant decrease in the recovery of galaxies with increasing redshift. This leads to lower recovery fractions of high mass clusters as many only exist at larger redshifts. The significant decline in the number of galaxies observed with the Survey strategy is due to gaps in the VIRUS IFU, where the galaxies are missed.}
	\label{fig: recovery}
\end{figure*}

@@

To confirm that measuring the underlying scatter is possible, after generating richness values we calculate the scatter of the cluster masses at fixed $\lambda$, $\sigma_{M|\lambda}$, by comparing the true, unperturbed cluster masses against the richness. We do recover the expected scatter, often, to well within 0.01 dex. We repeat the process with both assumed richness--mass relationships and recover the expected scatter in both instances.

>>>>

\section{Data and Mock Observations}\label{sec:Data}
In this section, we describe the data products and the techniques used to replicate the HETDEX survey. We use the information from a large mock galaxy catalog enhanced by the emission line properties of galaxies detected by the \textit{Sloan Digital Sky Survey} (SDSS; \citealt{York2000}) to create a realistic ``sky'' and ``observe'' it with a HETDEX-like observing strategy.

@@

Galaxy $M_r$ luminosities are added to the velocity peaks using Sub-halo Abundance Matching (ShAM) \citep{Reddick2013}, and the Adding Density Dependent Spectral Energy Distributions algorithm \citeeg{Cunha2012, Chang2015,Kwan2017} assign luminosities in the other bands. A $M_r$-density-SED relation is created using a SDSS training set, and for each mock galaxy the SED of a randomly selected training set galaxy which has a similar $M_r$ and density is assigned. The assigned SED is also used to determine additional $ugiz$ magnitudes. The result is a mock catalog containing 238 million galaxies with $\sdssr < 29$ mag and $z \leq 8.7$.

@@

\subsection{Conditional {\rm[\ion{O}{II}]} Flux Probability Distribution Functions}\label{sec: oii luminosity}
We use the SDSS Data Release 12 \citep{Alam2015} catalogs to assign [\ion{O}{II}] emission line strengths to the galaxies in the Buzzard catalog. We use 503,094 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{II}] line flux signal-to-noise of at least one. Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies, and the following SQL query selects the appropriate galaxies:
\begin{lstlisting}[language=SQL]
SELECT GAL.objid,
SELECT GAL.objid,
       GAL.u,
       GAL.err_u,
       GAL.g,
       GAl.err_g,
       GAL.r,
       GAL.err_r,
       GAL.i,
       GAl.err_i,
       GAL.z,
       GAL.err_z,
       g.oii_3726_flux,
       g.oii_3726_flux_err,
       s.z AS redshift
INTO   mydb.sdsstraining
FROM   galaxy AS GAL
       JOIN specobj AS s
         ON s.bestobjid = GAL.objid
       JOIN galspecline AS g
         ON g.specobjid = s.specobjid
WHERE  oii_3726_flux > oii_3726_flux_err
       AND oii_3726_flux_err > 0
       AND s.z BETWEEN 0.02 AND 0.2
       AND s.class = 'GALAXY'
       AND s.zwarning = 0
\end{lstlisting}

To assign an [\ion{O}{II}] luminosity to each galaxy in our catalog, we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy. We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{II}] luminosities, the right panel of Figure \ref{fig: oii sdss}. Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{II}] luminosity based on the distribution of SDSS galaxies in that bin. In very few cases (1.3\% of all galaxies), the $g-r$ and $M_r$ magnitudes of the galaxies in the Buzzard catalog do not overlap with the distributions in SDSS. For these objects, we assign them zero [\ion{O}{II}] flux, but this has no impact on our analysis. For catalog galaxies with have very few ($1\leq N<10$) SDSS galaxies in their respective bin, we assign it the mean [\ion{O}{II}] flux.

We investigate potential biases introduced by requiring an [\ion{O}{II}] signal-to-noise of at least one and find little to no affect. This is due to the way our galaxies are selected, utilizing both continuum measurements and line flux limits (see Section \ref{sec: hetdex} and \ref{sec: recovery} for details). Relaxing the signal-to-noise requirements leads to many more SDSS galaxies selected, but these galaxies are often removed during a data preprocessing step. \editorial{this needs to be edited and tightened up.}

@@

\subsection{Recovery of Cluster Members}\label{sec: recovery}
\begin{figure*}
	\includegraphics[width=0.8\textwidth]{figures/recovery.pdf}
	\caption[Recovery fractions for the Targeted and Survey observations.]{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and true cluster mass for the Targeted and Survey observing strategies. The Targeted observations include HETDEX line and continuum flux limits and have a unity fill factor. The Survey observations again include HETDEX-like flux limits but a HETDEX-like fill factor, 1/4.5. We require at least five galaxies to be detected for a cluster to be recovered. The shading indicates the mean recovery fraction for clusters within each small bin of redshift and cluster mass. We find a significant decrease in the recovery of galaxies with increasing redshift. This leads to lower recovery fractions of high mass clusters as many only exist at larger redshifts. The significant decline in the number of galaxies observed with the Survey strategy is due to gaps in the VIRUS IFU, where the galaxies are missed.}
	\label{fig: recovery}
\end{figure*}

@@

To confirm that measuring the underlying scatter is possible, after generating richness values we calculate the scatter of the cluster masses at fixed $\lambda$, $\sigma_{M|\lambda}$, by comparing the true, unperturbed cluster masses against the richness. We do recover the expected scatter, 0.1 dex in this case, with a mean absolute error of 0.015 dex after 12000 trials. We repeat the process with both assumed richness--mass relationships and recover the expected scatter in both instances.
